---
title: "R Notebook"
output:
  md_document:
    variant: markdown_github
---

#  Data manipulation in Jamovi

## Directions:
Complete each step of the assignment below.

## Package management in R

```{r}
# keep a list of the packages used in this script
packages <- c("tidyverse","rio","jmv")
```

This next code block has eval=FALSE because you don't want to run it when knitting the file. Installing packages when knitting an R notebook can be problematic.

```{r eval=FALSE}
# check each of the packages in the list and install them if they're not installed already
for (i in packages){
  if(! i %in% installed.packages()){
    install.packages(i,dependencies = TRUE)
  }
  # show each package that is checked
  print(i)
}
```

```{r}
# load each package into memory so it can be used in the script
for (i in packages){
  library(i,character.only=TRUE)
  # show each package that is loaded
  print(i)
}
```

A note about working with packages and functions in R:
When installing packages you may see notifications that SomePackage::function() masks OtherPackage::function().
What that means is that two different packages used the same function name. The functions may or may not do the same thing, but for whatever reason the pogrammers of each package happened to choose the same name for a function in their respective package. The last package installed will be the version of that function that will be used if only the function name is used in your R code. The SomePackage::function() notation with the colons in it means to use the function named function() from the package named SomePackage. I think I have decided when I write R code that I will always try to stick to that notation. That way it's very clear which package a desired function comes from and there will be no problems with masking if different packages used the same function name.

## Open data file

The rio package works for importing several different types of data files. We're going to use it in this class. There are other packages which can be used to open datasets in R. You can see several options by clicking on the Import Dataset menu under the Environment tab in RStudio. (For a csv file like we have this week we'd use either From Text(base) or From Text (readr). Try it out to see the menu dialog.)

```{r}
# import the Week3.rds dataset into RStudio

# Using the file.choose() command allows you to select a file to import from another folder.
# dataset <- rio::import(file.choose())

# This command will allow us to import the rds file included in our project folder.
dataset <- rio::import("Week3.rds")
```

## Get R code from Jamovi output

You can get the R code for most of the analyses you do in Jamovi.

1. Click on the three vertical dots at the top right of the Jamovi window.
2. Click on the Syndax mode check box at the bottom of the Results section.
3. Close the Settings window by clicking on the Hide Settings arrow at the top right of the settings menu.
4. you should now see the R code for each of the analyses you just ran.

## Run Jamovi code in RStudio

1. Copy the code for the descriptive statistics for the categorical variables in Jamovi and run the code block here in RStudio.

    + Right click on the code block in Jamovi.
    + Select Syntax - Copy
    + Paste it in the code block below.
    + You may need to change the name of the dataset to match the name of the data frame in RStudio. data = week3 (or the name of your data frame)
    
```{r}


```

2. Copy the code block for the descriptive statistics for the continuous variables and run it here in RStudio.

```{r}


```

## Some notes on Jamovi

* Some advantages of Jamovi

    + Jamovi takes some of the difficulty out of remembering commands to run statistical analyses by providing point and click menus.
    + Jamovi is freely available to anyone (and pretty easy to install) so it's easy to share output. (You can also export to other formats.)
    + The jmv package collects basic statistical anayses into a single package so it makes learning statistics in R a bit easier.
    + The Jamovi output is formatted very nicely. The tables are pretty much APA compliant.
    
* Some limitations of Jamovi

    + Jamovi does not allow you to make notes or write in the output like you can in RStudio. Interpreting output is as important as getting output in the first place. Making some notes to go along with what you analyze is pretty useful and important.
    + Jamovi does not currently have the wide variety of packages available which can be run in RStudio. It's a good idea to know both.
    + Jamovi is still undergoing significant development. There are some parts which may still be buggy. (Like importing the data set and having the empty columns at the beginning.)


## Save your output.
Save this assignment as a markdown file. 
    
## Submit your assignment.
Submit the output you just saved for your assignment.
